\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\parindent0em
\pagestyle{plain}
\usepackage{float}
\begin{document}
	\section{Introduction}
	RFDist is implemented and there are no known issues.
	\section{Implementation}
	The program is implemented with python. The trees are read by a Newick-parser from Bio.Phylo and afterwards translated into a self coded structure of nodes.\\
	The program uses Day's algorithm as explained in the lecture to compute the distance.\\
	We did the validation by testing the given trees and getting reasonable results in the experiments.\\
	You can run it by invoking main.py with python3 and either give the files that contains the trees as arguments or type their names when the program asks for them.
	\section{Experiments}
	\subsection{Experiment 1}
    Clustal Omega RapidNJ-QuickTree: 392 different intervals in each, thus 784 in total. Shared are  259 ;so we have a RF-Score of 266. \\
    
    Kalign RapidNJ-QuickTree: 386 different intervals in each, thus 772 in total. Shared are  291 ;so we have a RF-Score of 190 \\
    
    MUSCLE RapidNJ-QuickTree: 380 different intervals in each, thus 760 in total. Shared are  287 ;so we have a RF-Score of 186
    \subsection{Experiment 2}
    Clustal Omega RapidNJ-QuickTree: 392 different intervals in each, thus 784 in total. Shared are  259 ;so we have a RF-Score of 266. \\
    
    Kalign RapidNJ-QuickTree: 393 different intervals in each, thus 786 in total. Shared are  264 ;so we have a RF-Score of 258 \\
    
    MUSCLE RapidNJ-QuickTree: 388 different intervals in each, thus 776 in total. Shared are  288 ;so we have a RF-Score of 200
    \subsection{Experiment 3}
    Clustal Omega Normal RapidNJ - Clustal Omega Permuted RapidNJ :392 different intervals in each, thus 784 in total. Shared are  392 ;so we have a RF-Score of 0 \\
    Clustal Omega Normal QuickTree - Clustal Omega Permuted QuickTree :392 different intervals in each, thus 784 in total. Shared are  392 ;so we have a RF-Score of 0 \\
    
    Kalign Normal RapidNJ - Kalign Permuted RapidNJ :386 different intervals in each, thus 772 in total. Shared are  0 ;so we have a RF-Score of 772 \\
    Kalign Normal QuickTree - Kalign Permuted QuickTree :391 different intervals in each, thus 782 in total. Shared are  0 ;so we have a RF-Score of 782 \\

    MUSCLE Normal RapidNJ - MUSCLE Permuted RapidNJ :3380 different intervals in each, thus 760 in total. Shared are  0 ;so we have a RF-Score of 760 \\
    MUSCLE Normal QuickTree - MUSCLE Permuted QuickTree :393 different intervals in each, thus 786 in total. Shared are  0 ;so we have a RF-Score of 786 \\
\end{document}